\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-26 paper/main.tex
edits to paper through pg 3

The same computer code may not behave identically under different
circumstances.  For example, when code depends on external libraries,
different versions of those libraries may function differently.  Or
when CPU or GPU instruction sets differ across machines, the same
high-level code may be compiled into different machine instructions.
Because executing identical code does not guarantee identical
outcomes, code sharing in and of itself is often insufficient for
enabling researchers to reproduce each other's work.

Within the Python~\cite{vanR95} community, external
packages that are published in the most popular
repositories~\cite{Pyth03, cond15} are associated with version numbers
and tags that enable users to guarantee that they are installing
exactly the same code across different computing environments.
Despite that it is \textit{possible} to manually install the intended
version numbers of every dependency of a Python script or package, manually
tracking down those dependencies can impose a substantial burden on
the user.

@@

Researchers, programmers, and others have developed a broad
set of approaches and tools to facilitate code sharing and
reproducible outcomes (Fig.~\ref{fig:code-sharing}). At one
extreme, simply publishing a set of Python scripts (\texttt{.py} files) may
enable others to use or gain insights into the relevant work. Because
Python is installed by default on most modern operating systems, for
some projects this may be sufficient. Another popular approach
entails creating JSON files called Jupyter
notebooks~\cite{KluyEtal16} that comprise a mix of text, executable
code, and embedded media. Notebooks may call or import external
scripts or libraries in order to provide a more compact and readable
experience for users. Each of these systems (Python scripts and
notebooks) provides a convenient means of sharing code, with the
caveat that they do not specify the computing environment in which the
code is executed. Therefore the functionality of code shared using
these systems cannot be guaranteed across different computing
environments.

At another extreme, virtual machines~\cite{Gold74, AltiEtal05,
 Rose99} provide a hardware-level simulation of the desired system.
Virtual machines are typically isolated from the user's system, such
that installing or running software on a virtual machine does not
impact the user's primary operating system or computing environment.
Containers~\cite[e.g.,][]{Merk14, KurtEtal17} provide a similar
``isolated'' experience. Although containerized environments do not
specify hardware-level operations, they are typically packaged with a
complete operating system, in addition to a complete copy of Python
and any relevant package dependencies. Virtual
environments~\cite[e.g.,][]{Anac12} also provide a computing
environment that is largely separated from the user's main
environment. They incorporate a copy of Python and the target
software's dependencies, but virtual environments do not specify or
reproduce an operating system for the runtime environment. Each of
these systems (virtual machines, containers, and virtual environments)
guarantees (to differing degrees---at the hardware level, operating
system level, and Python environment level, respectively) that the
relevant code will run similarly for different users. However, each
of these systems also relies on additional software that can be
resource intensive or burdensome to install or configure.

>>>>

The same computer code may not behave identically under different
circumstances.  For example, when code depends on external libraries,
different versions of those libraries may function differently.  Or
when CPU or GPU instruction sets differ across machines, the same
high-level code may be compiled into different machine instructions.
Because executing identical code does not guarantee identical
outcomes, code sharing alone is often insufficient for
enabling researchers to reproduce each other's work, or to collaborate on
projects involving data collection or analysis.

Within the Python~\cite{vanR95} community, external
packages that are published in the most popular
repositories~\cite{Pyth03, cond15} are associated with version numbers
and tags that allow users to guarantee they are installing
exactly the same code across different computing environments \cite{CoghStuf13}.
Despite that it is \textit{possible} to manually install the intended
version of every dependency of a Python script or package, manually
tracking down those dependencies can impose a substantial burden on 
the user and make room for mistakes. Further, when dependency versions 
are left unspecified, replicating the original computing environment 
becomes difficult or impossible.

@@

Computational researchers and other programmers have developed a broad
set of approaches and tools to facilitate code sharing and
reproducible outcomes (Fig.~\ref{fig:code-sharing}). At one
extreme, simply distributing a set of Python scripts (\texttt{.py} files) may
enable others to use or gain insights into the relevant work. Because
Python is installed by default on most modern operating systems, for
some projects, this may be sufficient. Another popular approach
entails creating Jupyter
notebooks~\cite{KluyEtal16} that comprise a mix of text, executable
code, and embedded media. Notebooks may call or import external
scripts or libraries---even intersperse snippets of other programming 
or markup languages---in order to provide a more compact and readable
experience for users. Each of these systems (Python scripts and
notebooks) provides a convenient means of sharing code, with the
caveat that they do not specify the computing environment in which the
code is executed. Therefore the functionality of code shared using
these systems cannot be guaranteed across different users or setups.

At another extreme, virtual machines~\cite{Gold74, AltiEtal05,
 Rose99} provide a hardware-level simulation of the desired system.
Virtual machines are typically isolated such
that installing or running software on a virtual machine does not
impact the user's primary operating system or computing environment.
Containers~\cite[e.g.,][]{Merk14, KurtEtal17} provide a similar
``isolated'' experience. Although containerized environments do not
specify hardware-level operations, they are typically packaged with a
complete operating system, in addition to a complete copy of Python
and any relevant package dependencies. Virtual
environments~\cite[e.g.,][]{Anac12} also provide a computing
environment that is largely separated from the user's main
environment. They incorporate a copy of Python and the target
software's dependencies, but virtual environments do not specify or
reproduce an operating system for the runtime environment. Each of
these systems (virtual machines, containers, and virtual environments)
guarantees (to differing degrees---at the hardware level, operating
system level, and Python environment level, respectively) that the
relevant code will run similarly for different users. However, each
of these systems also relies on additional software that can be
resource intensive or burdensome to install or configure.
